\subsection{Implementation}
The website is constructed using \lref{https://www.php.net/}{PHP 8.1} on \lref{https://httpd.apache.org/}{Apache}, \lref{https://www.php.net/manual/en/book.mysqli.php}{mysqli}, and \lref{https://developers.google.com/chart/}{Google Charts} through \lref{https://developer.mozilla.org/en-US/docs/Web/JavaScript}{JavaScript}.
The development version is a docker image run inside the WebInterface docker compose project.
The files in \bashline{server/html} in the WebInterface repository can be copied to a host for deployment.

\subsection{Authentication}
All website pages are protected by Shibboleth (the development version uses generic .htaccess files).
Access to the database is controlled through locally stored credentials.
It is assumed that any user with access to the underlying environment,
    or can log into the webpage,
    should be given full control of the system and access to all secrets.
The two users constructed for interacting with the database are to protect against bugs,
    not to act as a protective measure.

\subsection{Functionality}
The website has full admin access to the database.
All actions are built upon a consistent main display page that is meant for desktop use.
Administrative changes (i.e. blocking a user) are performed through PHP form submissions.
Live data graphs are constructed through continuous JavaScript actions.
Any SQL commands outside of the prebuilt set should be performed with a separate MariaDB interactive client.